---
title: "Pratical Machine Learning - Course Project"
author: "Mauro Ricardo da Silva"
date: "16 de janeiro de 2018"
output: html_document
---

The model was built after the analisys in dataset. In this analisys was possible identify attributes without values. The next step was cleaning the dataset e slicing in training and testing set. The first dataset was submitted to a training in a learning model based in random forest. The testing set, when submitted to model, returned 99,5% accuracy.

## Downloading the files

This URLs was supplied by the Course Project Instructions.

```{r downloading}
URL_training      <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
destfile_training <- "pml-training.csv"

URL_test      <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
destfile_test <- "pml-test.csv"

if(!file.exists(destfile_training)){
  download.file(URL_training, destfile_training)
}


if(!file.exists(destfile_test)){
  download.file(URL_test, destfile_test)
}
```

## Loading and cleaning data

The pml-test file was converted into validation set.

```{r cleaning}
pml_training <-  read.csv("pml-training.csv")
pml_training <- pml_training[, c(8:11, 37:49, 60:68, 84:86, 102, 113:124, 140, 151:160)]

pml_testing <-  read.csv("pml-test.csv")
validating  <- pml_testing[, c(8:11, 37:49, 60:68, 84:86, 102, 113:124, 140, 151:160)]
```

## Slicing data in training and test datasets

The training set was divided into 2 parts. 75% into a training set and 25% into a testing set.

```{r slicing}
library(caret)
library(kernlab)

inTrain <- createDataPartition(y = pml_training$classe, p = 0.75, list = FALSE)

training <- pml_training[inTrain, ]
testing <- pml_training[-inTrain, ]
dim(training)
```

## creating predicition model 

The choice by Random forest was motivated by the large number of the attributes. In the first iteration the choice matched the expectation presenting about 99,5% accuracy.

```{r modeling}
control          <- trainControl(method = "cv",number = 4, allowParallel = TRUE)
model            <- train(classe ~ ., data=training, method = "rf" , trControl = control)
predict          <- predict(model, testing)
confusionMatrix  <- confusionMatrix(testing$classe, predict)

confusionMatrix
accuracy <- confusionMatrix$overall[1]

error <- (1 - sum(predict == testing$classe) / length(predict))
error
```

## making prediction 

```{r predicting}
result  <- predict(model, validating)
result
```
